---
page-layout: full
listing: 
  - id: recent-projects
    contents: "posts/**/*.qmd"
    page-size: 6
    type: grid
  - id: recent-blog
    contents: "posts/**/*.qmd"
    page-size: 8
    type: table
---

::::: {#id1 .jumbotron .column-screen-inset style="margin: 0; padding: 0;" layout="[40,65]"}

  <div class="container">
  <div style="margin-left: 20px; margin-top: 30px; position: absolute; top: 180px; left: 150px;" >
  <h1 style="margin-top: 20px; margin-bottom: 10px; font-weight: 500; color: white;">Welcome</h1>
  <p style="display: block; margin-block-start: 1rem; margin-block-end: 1rem; margin-inline: 0; margin-bottom: 15px;font-size: 21px; font-weight; 200; color: white;">To Data Discoveries: Unveiling the Hidden Stories Through Analytics</p>
  <p><a class="btn btn-success btn-xlg" href="projects.qmd" role="button" style="color: #fff; background-color: #051094; border-color: #fff;">Learn more</a></p>
  </div>
  </div>
  
:::::

## Services {.column-page}

::: {.column-page}

As an exprienced business data analyst and data scientist, my goal is to leverage advanced analytics to unearth actionable insights that drive tangible business growth, optimizing processes, enhancing customer experiences, and maximizing ROI

I am experienced in machine learning, supervised and unsupervised algorithms and use data visualization techniques to present the results. I use SQL, R, Python, PowerBI for my data projects.

:::

::: {.column-page layout="[[50,50],[50,50],[50,50]]" layout-valign="top" style="margin-top: 3px; margin-bottom: 0; padding: 1px;"}

```{r}
#| echo: false
#| warning: false
#| error: false

library(htmltools)

tags$div(class="col-xs-12 col-sm-6 service icon-container",
        tags$div(class="col-xs-2 icon",
          tags$img(src = "/data_analysis.png", alt="Icon advice and coaching projects", width="17%"),
        
        tags$div(class="col-xs-10 description", tags$h3("Data Analysis"),
          tags$p("I specialize in unlocking data's power across ecommerce, FMCG, and pharmaceuticals, transforming it into crucial insights that empower informed decisions, guide through challenges, and drive business growth",tags$br(),"(",
                        tags$a(href="#", "examples"), ")")) )
        )
```

```{r}
#| echo: false
#| warning: false
#| error: false

# "C:\Users\oseji.victor\Documents\My_Portfolio\Dashboard.jpeg"

tags$div(class="col-xs-12 col-sm-6 service icon-container",
        tags$div(class="col-xs-2 icon",
          tags$img(src = "/dashboard.png", alt="Icon advice and coaching projects", width="17%"),
        tags$div(class="col-xs-10 description", style="justify-content: flex-start;",
                 tags$h3("Data Visualization"),
                 tags$p("As an experienced data scientist, I specialize in comprehensive data analysis and impactful visualization using tools like Excel, R Shiny, Quarto, R Markdown, and PowerBI to empower stakeholders in making well-informed decisions",tags$br(),"(",
                        tags$a(href="#", "examples"), ")"))  )
        )
```

```{r}
#| echo: false
#| warning: false
#| error: false

tags$div(class="col-xs-12 col-sm-6 service icon-container",
        tags$div(class="col-xs-2 icon",
          tags$img(src = "/predictive.png", alt="Icon data analysis", width="17%"),
        tags$div(class="col-xs-10 description", tags$h3("Predictive Analytics"),
                 tags$p("I am a skilled data scientist experienced in using advanced machine learning to predict trends, extract insights from complex data, and drive growth through data-driven strategies for competitive advantage in dynamic markets",tags$br(),"(",
                        tags$a(href="#", "examples"), ")")) ) )

```

```{r}
#| echo: false
#| warning: false
#| error: false

tags$div(class="col-xs-12 col-sm-6 service icon-container",
        tags$div(class="col-xs-2 icon",
          tags$img(src = "/customer_analytics.png", alt="Icon advice and coaching projects", width="17%"),
        tags$div(class="col-xs-10 description", tags$h3("Customer Understanding"),
                 tags$p("I provide tailored customer understanding solutions using advanced data analysis and machine learning, enabling businesses to enhance decision-making, optimize experiences, and foster lasting customer relationships for competitive advantage.",tags$br(),"(",
                        tags$a(href="#", "examples"), ")")) ) )
```

```{r}
#| echo: false
#| warning: false
#| error: false

tags$div(class="col-xs-12 col-sm-6 service icon-container",
        tags$div(class="col-xs-2 icon",
          tags$img(src = "/collaboration.png", alt="Icon data analysis", width="17%"),
        tags$div(class="col-xs-10 description", tags$h3("Collaboration"),
                 tags$p("I excel in extracting valuable insights from complex datasets and effectively translating them into actionable business strategies, enabling informed cross-domain decisions and fostering cohesive teamwork towards shared objectives.",tags$br(),"(",
                        tags$a(href="#", "examples"), ")"))) )

```

```{r}
#| echo: false
#| warning: false
#| error: false

tags$div(class="col-xs-12 col-sm-6 service icon-container",
        tags$div(class="col-xs-2 icon",
          tags$img(src = "/optimize3.png", alt="Icon advice and coaching projects", width="17%"),
        tags$div(class="col-xs-10 description", tags$h3("Process Optimization"),
                 tags$p("I provide comprehensive business process optimization services by utilizing data-driven insights to streamline operations, reduce costs, and drive sustainable growth through strategic implementation and tailored strategies",tags$br(),"(",
                        tags$a(href="#", "examples"), ")")) ) )
```

:::

## Recent Projects

Explore a diverse collection of projects that showcase my skills and passion for data science:

::: {#recent-projects .column-page}
:::

## Recent Blog Posts

Dive into my blog where I share data tips, tutorials, and insights that empower you to embark on your own data journey. Explore resources that will boost your data literacy and analytical prowess

::: {#recent-blog .column-page}
:::
